Generalized Plackett-Luce Likelihoods

### 2022-09-28 inst/jss_hyper3.Rnw
fixes #160
further work on issue #157

Existing \code{hyper2} formalism as described by \citet{hankin2017}
cannot represent this likelihood function, because
Equation~\ref{hyper2likelihood} uses sets as the indexing elements,
and in this case we need multisets\footnote{Note that the version of
\code{hyper2} presented by \citet{hankin2017} and reviewed
by~\cite{turner2020} used integer-valued sets together with a print
method that used a complicated mapping system from integers to
competitor names.  Current methodology [following commit
  \code{51a8b46}] is to use sets of character strings which represent
the competitors directly; this allows for easier combination of
observations including different competitors.}.  The declarations

>>>>

\subsection{Computational methodology for generalized Plackett-Luce likelihood functions}

Existing \code{hyper2} formalism as described by \citet{hankin2017}
cannot represent Equation~\ref{plackettluce}, because
Equation~\ref{hyper2likelihood} uses sets as the indexing elements,
and in this case we need multisets\footnote{Note that the version of
\code{hyper2} presented by \citet{hankin2017} and reviewed
by~\cite{turner2020} used integer-valued sets together with a print
method that used a complicated mapping system from integers to
competitor names.  Current methodology [following commit
  \code{51a8b46}] is to use sets of character strings which represent
the competitors directly; this allows for easier combination of
observations including different competitors.}.  The declarations
